\thesistitle

### 2019-04-10 main.tex
Code clone harmfulness

\subsection{Relevance to clone refactoring}
Higher type clones are not only harder to detect, but also harder to refactor. How to refactor clones is heavily dependent on it's context and type. Method-level Type I clones can commonly be refactored by using the ``Extract method'' refactoring \cite{kodhai2013method}.

@@

\chapter{Clone detection}

>>>>

\subsection{Relevance to clone refactoring}
Higher type clones are not only harder to detect, but also harder to refactor. How to refactor clones is heavily dependent on their context and type. Kodhai et al \cite{kodhai2013method} describe different refactorings that can be performed to deal with clones.

@@

\section{Code clone harmfulness}
There has been a lot of discussion whether code clones should be considered harmful.

Most papers view clones as harmful regarding program maintainability. \textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well. Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work.''} \cite{ostberg2014automatically}

However, the harmfulness of clones depends on a lot of factors. A paper by Kapser et al \cite{kapser2006cloning} describes several patterns of cloning that may not be considered harmful. In this paper Kapser names examples where eliminating clones would compromise other important program qualities. Another study by Jarzabek et al \cite{jarzabek2010clones} categorized ``Essential clones'': clones that are essential because of the solution that is being modelled by the program. Overall, many of the benefits of code clones do not apply to most modern object-oriented programming languages.

\section{State-of-the-art}
There have been some papers that take some steps towards code clone refactoring.

\chapter{Clone detection}
Clone detection is
